Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

Beyond solving the garbage collection in concurrent programming environment, the main objectives of this thesis are to design garbage collectors for shared and distributed memory system that satisfy the following properties :
\begin{enumerate}
	\item Concurrent garbage collectors (Less pause time)
	\item Multi-collector garbage collection
	\item No global synchronization (High Throughput)
	\item Locality based garbage collection
	\item Scalable
	\item Promptness
	\item Safety
	\item Completeness
\end{enumerate}

There are no garbage collection algorithms available for shared and distributed memory systems that satisfy all the above-mentioned properties.  This thesis focuses on designing novel garbage collector with significant improvement. Apart from garbage collection, the ideas presented in the thesis will be of use to solve other theoretical problems in distributed computing like dynamic reachability, breaking cycle, detecting cycles in graph, data aggregation in the sensor network, broken network detection in sensor networks.

@@

Concurrent garbage collectors work simultaneously with the application. The application will not experience any pause during execution to scan the memory. They

@@

\paragraph{Multi-collector Garbage :}
Multi-collector garbage collectors are multiple independent garbage collector thread / process that works independently on the heap to identify garbage. These collectors utilize multiple processors when there is a lot of compute resources being underutilized. In shared memory systems, when multiple processors are underutilized, this property helps to utilize processor cycles better. Apart from the processor utilization, the throughput of garbage collectors can be increased by multi-collector garbage collectors. These multi-collector garbage collector threads / processes communicate among themselves through memory in shared memory systems and through messages in distributed memory systems.

>>>>

Beyond solving the garbage collection problem in a concurrent programming environment, the objectives of this thesis are to design garbage collectors for shared and distributed memory system that satisfy the following properties :
\begin{enumerate}
	\item Concurrent garbage collectors (Less pause time)
	\item Multi-collector garbage collection (Parallel)
	\item No global synchronization (High Throughput)
	\item Locality-based garbage collection
	\item Scalable
	\item Prompt
	\item Safety
	\item Complete
\end{enumerate}

There are no garbage collection algorithms available for shared and distributed memory systems that satisfy all the above-mentioned properties.  This thesis focuses on designing a novel garbage collector with significant improvements. Apart from garbage collection, the ideas presented in the thesis will be of use to solve other theoretical problems in distributed computing like dynamic reachability, breaking cycles, detecting cycles, data aggregation in a sensor network, broken network detection in a sensor networks.

@@

Concurrent garbage collectors work simultaneously with the application. The application will not experience any pauses during execution to scan memory. They

@@

\paragraph{Multi-collector Garbage Collection :}
Multi-collector are multiple independent garbage collectors thread / process that works independently on the heap to identify garbage. These collectors utilize multiple processors when there is a lot of compute resources being underutilized. In shared memory systems, when multiple processors are underutilized, this property helps to utilize processor cycles better. Apart from the processor utilization, the throughput of garbage collectors can be increased by multi-collector garbage collectors. These multi-collector garbage collector threads / processes communicate among themselves through memory in shared memory systems and through messages in distributed memory systems.
